On the means, costs, and system-level impacts of 24/7 carbon-free energy procurement

### 2023-10-27 manuscript/manuscript.tex
license: add reuse compatibility
project: initial run pre-commit against all files
manuscript: update acknowledgements

@@

This work is an independent follow-up to the prior public report by the authors \cite{riepin-zenodo-systemlevel247} with an updated model, updated system-wide assumptions, and additional analysis of the results. The prior public report was supported by a research grant from Google LLC.

@@

>>>>

% SPDX-FileCopyrightText: 2023 Iegor Riepin, Tom Brown
%
% SPDX-License-Identifier: CC-BY-4.0

@@

@@

Iegor Riepin was supported by the research grant from Google LLC.

This work is a follow-up to the prior public report by the authors \cite{riepin-zenodo-systemlevel247} with an updated model, updated system-wide assumptions, and additional analysis of the results.
